A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-13 manuscript.Rmd
add reviewer thanks and added contributors

authornote: |
   We are grateful to Julia Delius for her helpful assistance in language and style editing. We thank all contributors of our GitHub repository for helpful feedback on the paper. This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompanying GitHub repository: [https://github.com/aaronpeikert/reproducible-research/](https://github.com/aaronpeikert/reproducible-research/). This particular document was created from the commit with the hash `"`r system2("git", "rev-parse --short HEAD", stdout = TRUE)`"`. To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the GitHub repository of our paper at [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).

@@

The `--rm` flag means that the state of the container after the command finishes is not saved. The `-it` flag tells Docker to accept inputs and return outputs to the terminal. Interacting with docker this way is especially useful when using `R` as a command because you then have access to the standard R terminal. This is the command to start an interactive R session inside a Docker image called `reproducible-research` (see Figure \@ref{fig:docker-r-terminal} for a screenshot):

>>>>

authornote: |
   We are grateful to Julia Delius for her helpful assistance in language and style editing. We thank the reviewers and all contributors of our GitHub repository for helpful feedback on the paper. This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompanying GitHub repository: [https://github.com/aaronpeikert/reproducible-research/](https://github.com/aaronpeikert/reproducible-research/). This particular document was created from the commit with the hash `"`r system2("git", "rev-parse --short HEAD", stdout = TRUE)`"`. To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the GitHub repository of our paper at [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).

@@

The `--rm` flag means that the state of the container after the command will have finished is not going to be saved. The `-it` flag tells Docker to run the command interactively, that is, to accept keyboard inputs and return outputs to the terminal. For example, this is the command to start an interactive R session inside a Docker image called `reproducible-research` (see Figure \@ref{fig:docker-r-terminal} for a screenshot):
